Verifying Demonstrations

### 2018-11-16 paper/system-model.tex
adds some comments, moves gvt id remarks from system model to discussion

Throughout this paper, each time we refer to a participant, such as Alice, we actually mean a personal device that can perform cryptographic operations and communicate with other local devices on Alice's behalf. 
Furthermore, we assume that each participant has a digital certificate signed by the \ac{CA}.
For instance, we could use the cryptographic keys of any national electronic identity system, identity card or passport.
This assumption is needed to prevent Sybil attacks~\cite{SybilAttack}, which would have a disastrous effect on the crowd-counting estimation\footnote{
Of course, this has for consequence that the \ac{CA} can perform a Sybil attack on the system.
Thus, if the \ac{CA} is controlled by the government, no counts in favor of the government can be be trusted.
}.

>>>>

Throughout this paper, each time we refer to a participant, such as Alice, we actually mean a personal device that can perform cryptographic operations and communicate with other local devices on Alice's behalf. 
Furthermore, we assume that each participant has a digital certificate of her identity signed by a \ac{CA}.
